Reduced plasticity and relative variance in physiological rates of ectotherm populations under climate change

### 2024-06-21 ms.qmd
Fixed up fig-4 which is now in supp to jive with fig-5 in main MS

Theoretical models highlight the importance of environmental predictability in selecting for plastic responses. However, capturing environmental predictability is challing given that it is unclear which timescale one should select. For example, is it more important to look at correlation between temperatures monthly or seasonally. In addition, such temporal resolution will likely depend on the species in question given that for some species fine-grained thermal predictability maybe more important compared to others.

@@

```{r, fig-4}
#| label: fig-4
#| fig-align: center
#| fig-cap: "Predicted mean (thick black line) $lnRR_{Q_{10}}$ as a function of the Thermal Coefficient of Variation (CV) (A) and thermal predictability (B) for wild populations across marine, freshwater and terrestrial habitats. Dashed lines indicate 95% confidence intervals and dotted lines indicate 95% prediction intervals. Model slope ($\\beta$) along with the 95% CI and $p_{MCMC}$ value is shown for each habitat."

size_axis = 18
# lnRR ACF

 col <- c("#0871B9", "#F3B40D", "#1BB908")

 dat_text2rr <- data.frame(label = c(text(slope_f_3.8), text(slope_m_3.8), text(slope_t_3.8)),
                      label2 = c(text(slope_f_3.8, b = FALSE), text(slope_m_3.8,b = FALSE), text(slope_t_3.8,b = FALSE)),
                      p = c(p_text(slope_f_3.8), p_text(slope_m_3.8), p_text(slope_t_3.8)),
                      condition = c("f", "m", "t"),
                      x = rep(-2.8, 3),
                      y = rep(-1.2, 3))

p8.2 <- bubble_plot(model3.8, mod = "acf_all_c", group = "record_num", by = "habitat",  ylab = TeX("$lnRR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k = FALSE) + 
theme_classic() + 
scale_fill_manual(values = c(col)) + 
geom_text(data = dat_text2rr, aes(x = x+1, y = y, label =label), size = 5) + 
geom_text(data = dat_text2rr, aes(x = x+1, y = y-0.3, label =label2), size = 5) +
geom_text(data = dat_text2rr, aes(x = x+1, y = y-0.65, label = p), size = 5) +
theme(legend.position = "bottom", 
      strip.background = element_blank(), 
      strip.text = element_blank(), 
      axis.text = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis),
      legend.text = element_text(size = 16),
      legend.title = element_text(size = 16))

# lnCVR ACF
dat_text2cvr <- data.frame(label = c(text(slope_f_4.8), text(slope_m_4.8), text(slope_t_4.8)),
                      label2 = c(text(slope_f_4.8, b = FALSE), text(slope_m_4.8,b = FALSE), text(slope_t_4.8,b = FALSE)),
                      p = c(p_text(slope_f_4.8), p_text(slope_m_4.8), p_text(slope_t_4.8)),
                      condition = c("f", "m", "t"),
                      x = rep(-2.8, 3),
                      y = rep(-4, 3))

p9.2 <- bubble_plot(model4.8, mod = "acf_all_c", group = "record_num", by = "habitat",  ylab = TeX("$lnCVR_{Q_{10}}$"), xlab = "Thermal Predictability", condition.nrow = 1, k = FALSE) + 
theme_classic() + 
scale_fill_manual(values = c(col)) + 
geom_text(data = dat_text2cvr, aes(x = x+1, y = y, label = label), size = 5) + 
geom_text(data = dat_text2cvr, aes(x = x+1, y = y-0.6, label = label2), size = 5) +
geom_text(data = dat_text2cvr, aes(x = x+1, y = y-1.2, label = p), size = 5) +
theme(legend.position = "bottom", 
      strip.background = element_blank(), 
      strip.text = element_blank(), 
      axis.text = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis),
      legend.text = element_text(size = 16),
      legend.title = element_text(size = 16))

p8.1.2 <- (p8.1 / p8.2) + plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 20))

ggsave(p8.1.2, width = 8.2, height = 8.7, filename = "./output/figures/fig8.png")

  p8.1.2 <- image_read("./output/figures/fig8.png")
  p8.1.2 
```
#### *Publication bias analysis*

>>>>

Theoretical models highlight the importance of environmental predictability in selecting for plastic responses. However, capturing environmental predictability is challenging given that it is unclear which timescale one should select. For example, is it more important to look at correlation between temperatures monthly or seasonally. In addition, such temporal resolution will likely depend on the species in question given that for some species fine-grained thermal predictability maybe more important compared to others.

@@

```{r, fig-4}
#| label: fig-4
#| fig-align: center
#| fig-cap: "Predicted mean acclimation (thick black line) $lnRR_{Q_{10_{acclim}}}$ (A) and $lnCVR_{Q_{10_{acclim}}}$ (B) as a function of the Thermal Predictability for wild populations across marine, freshwater and terrestrial habitats. Dashed lines indicate 95% confidence intervals and dotted lines indicate 95% prediction intervals. Model slope ($\\beta$) along with the 95% CI and $p_{MCMC}$ values for the slopes are shown for each habitat."

####################
# lnRR ACF
####################
 dat_textacf <- data.frame(label = c(text(slope_f), text(slope_m), text(slope_t)),
                      label2 = c(text(slope_f, b = FALSE), text(slope_m,b = FALSE), text(slope_t,b = FALSE)),
                      p = c(p_text(slope_f), p_text(slope_m), p_text(slope_t)),
                      title = c("Freshwater", "Marine", "Terrestrial"), 
                      condition = c("f", "m", "t"),
                      x = rep(0, 3))
y_adj = -3
# Terrestrial
  p_t_rr_acf <-  bubble_plot(model3.9_t, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}$"), xlab = "Thermal Predictability", g = TRUE) + 
    geom_point(data = lnRRQ10_data_wild_acclim_t, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[3], colour = "black", stroke = 0.2, shape = 21) + labs(title = dat_text$title[3]) +
  annotate("text", x = dat_text$x[3], y = y_adj, label = TeX(dat_text$p[3]), size = 8) +
  annotate("text", x = dat_text$x[3], y = y_adj + 0.5, label = TeX(dat_text$label2[3]), size = 8) +
  annotate("text", x = dat_text$x[3], y = y_adj + 1, label = TeX(dat_text$label[3]), size = 8) +
theme(axis.text = element_text(size = size_axis), 
      axis.text.y = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis),
      axis.title.x = element_blank(),
      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3,3)

# Marine
p_m_rr_acf <-  bubble_plot(model3.9_m, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}"), xlab = "Thermal Predictability", g = TRUE) + 
    geom_point(data = lnRRQ10_data_wild_acclim_m, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[2], colour = "black", stroke = 0.2, shape = 21) +  labs(title = dat_text$title[2]) +
  annotate("text", x = dat_text$x[2]-0.5, y = y_adj, label = TeX(dat_text$p[2]), size = 8) +
  annotate("text", x = dat_text$x[2]-0.5, y = y_adj+0.5, label = TeX(dat_text$label2[2]), size = 8) +
  annotate("text", x = dat_text$x[2]-0.5, y = y_adj+1, label = TeX(dat_text$label[2]), size = 8) +
theme(axis.text = element_text(size = size_axis), 
      axis.text.y = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis), 
      axis.title.x = element_blank(),
      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3, 3)

# Freshwater
p_f_rr_acf <-  bubble_plot(model3.9_f, mod = "cv_c", group = "spp", ylab = TeX("$lnRR_{Q_{10_{acclim}}}"), xlab = "Thermal Predictability", g = TRUE) + 
    geom_point(data = lnRRQ10_data_wild_acclim_f, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[1], colour = "black", stroke = 0.2, shape = 21) +  labs(title = dat_text$title[1]) +
  annotate("text", x = dat_text$x[1]+0.6, y = y_adj, label = TeX(dat_text$p[1]), size = 8) +
  annotate("text", x = dat_text$x[1]+0.6, y = y_adj+0.5, label = TeX(dat_text$label2[1]), size = 8) +
  annotate("text", x = dat_text$x[1]+0.6, y = y_adj+ 1, label = TeX(dat_text$label[1]), size = 8) +
theme(axis.text = element_text(size = size_axis), 
      axis.text.y = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis), 
      axis.title.x = element_blank(),
      plot.title = element_text( size = 36, hjust = 0)) + ylim(-3, 3)

####################
# lnCVR CV
####################
dat_textcvr_acf <- data.frame(label = c(text(slope_f_4.9), 
                                 text(slope_m_4.9), 
                                 text(slope_t_4.9)),
                      label2 = c(text(slope_f_4.9, b = FALSE), 
                                 text(slope_m_4.9,b = FALSE), 
                                 text(slope_t_4.9,b = FALSE)),
                           p = c(p_text(slope_f_4.9), 
                                 p_text(slope_m_4.9), 
                                 p_text(slope_t_4.9)),
                       title = c("Freshwater", "Marine", "Terrestrial"), 
                      condition = c("f", "m", "t"),
                      x = rep(0, 3),
                      y = rep(-4, 3))

# Freshwater
  yadj2 = -6
  x_f = 0.6
  p_f_cv_acf <-  bubble_plot(model4.9_f, mod = "cv_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Predictability", g =FALSE, k = FALSE) + 
      geom_point(data = lnCVRQ10_data_wild_acclim_f, aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), fill = col[1], colour = "black", stroke = 0.2, shape = 21) + 
    annotate("text", x = dat_textcvr$x[1]+x_f, y = yadj2, label = TeX(dat_textcvr$p[1]), size = 8) +
    annotate("text", x = dat_textcvr$x[1]+x_f, y = yadj2+0.8, label = TeX(dat_textcvr$label2[1]), size = 8) +
    annotate("text", x = dat_textcvr$x[1]+x_f, y = yadj2+1.6, label = TeX(dat_textcvr$label[1]), size = 8) +
  theme(axis.text = element_text(size = size_axis), 
        axis.text.y = element_text(size = size_axis), 
        axis.title = element_text(size = size_axis), 
        plot.title = element_text(face = "bold", size = 36, hjust = 0.5)) + 
    ylim(-6, 3.5)

# Marine
  x_m = -0.4
  p_m_cv_acf <-  bubble_plot(model4.9_m, mod = "cv_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Predictability", g =FALSE, k = FALSE) + 
    geom_point(data = lnCVRQ10_data_wild_acclim_m, 
                 aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), 
                 fill = col[2], colour = "black", stroke = 0.2, shape = 21) + 
    annotate("text", x = dat_textcvr$x[1]+x_m, y = yadj2, label = TeX(dat_textcvr$p[2]), size = 8) +
    annotate("text", x = dat_textcvr$x[1]+x_m, y = yadj2+0.8, label = TeX(dat_textcvr$label2[2]), size = 8) +
    annotate("text", x = dat_textcvr$x[1]+x_m, y = yadj2+1.6, label = TeX(dat_textcvr$label[2]), size = 8) +
    theme(axis.text = element_text(size = size_axis), 
        axis.text.y = element_text(size = size_axis), 
        axis.title = element_text(size = size_axis), 
        plot.title = element_text(face = "bold", size = 36, hjust = 0.5)) + 
    ylim(-6, 3.5)

x_t = 0
p_t_cv_acf <-  bubble_plot(model4.9_t, mod = "cv_c", group = "spp", ylab = TeX("$lnCVR_{Q_{10_{acclim}}}$"), xlab = "Thermal Predictability", g = FALSE, k = FALSE) + 
  geom_point(data = lnCVRQ10_data_wild_acclim_t, 
               aes(x = cv_c, y = effect_size, size = 1/sqrt(V)), 
               fill = col[3], colour = "black", stroke = 0.2, shape = 21) +
  annotate("text", x = dat_textcvr$x[3]+x_t, y = yadj2, label = TeX(dat_textcvr$p[3]), size = 8) +
  annotate("text", x = dat_textcvr$x[3]+x_t, y = yadj2+0.8, label = TeX(dat_textcvr$label2[3]), size = 8) +
  annotate("text", x = dat_textcvr$x[3]+x_t, y = yadj2+1.6, label = TeX(dat_textcvr$label[3]), size = 8) +
  theme(axis.text = element_text(size = size_axis), 
      axis.text.y = element_text(size = size_axis), 
      axis.title = element_text(size = size_axis), 
      plot.title = element_text(face = "bold", size = 36, hjust = 0.5)) + 
  ylim(-6, 3.5)

p_cv_acf <- (p_t_rr_acf + p_m_rr_acf + p_f_rr_acf) / (p_t_cv_acf + p_m_cv_acf + p_f_cv_acf) + plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 36))

ggsave(p_cv_acf, width = 18, height = 10, filename = "./output/figures/fig_p_cv_acf_r1.pdf")

  p_cv <- image_read("./output/figures/fig_p_cv_r1.png")
  p_cv 
```
#### *Publication bias analysis*
